Evaluating Cloud-Optimized HDF5 for NASA’s ICESat-2 Mission

### 2025-01-16 paper.qmd
rewrite sensence to change to present tense

The most recent version of the Hierarchical Data Format is HDF5, a common archival format for n-dimensional scientific data; it has been utilized to store valuable information from astrophysics to earth sciences and everything in between. As flexible and powerful as HDF5 can be, it comes with big trade-offs when it’s accessed from remote storage systems.

>>>>

The most recent version of the Hierarchical Data Format is HDF5, a common archival format for n-dimensional scientific data. HDF5 is used to store data from astrophysics to earth sciences and everything in between. However, as flexible and powerful as HDF5 can be, it comes with big trade-offs when it’s accessed from remote storage systems.
